Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-04-04 7.GWAS/7.chi-square.tex
many changes... Chapter 4 intro WIP

\begin{theorem} \label{thm:chi-squared-exact-boundary}
Consider the high-dimensional chi-squared model \eqref{eq:model-chisq-Chapter6} with signal sparsity and size as described in \eqref{eq:signal-sparsity} and \eqref{eq:signal-size}.
The function 
\begin{equation} \label{eq:exact-boundary-chisquared}
    g(\beta) = \left(1 + \sqrt{1-\beta}\right)^2
\end{equation}
characterizes the phase transition of exact support recovery problem.
Namely, the following two results hold.\\

{\rm (i)} If $\underline{r} > {{g}}(\beta)$, then Bonferroni's, Sid\'ak's, Holm's, and Hochberg's procedures with slowly vanishing (see Definition \ref{def:slowly-vanishing}) nominal FWER levels all achieve asymptotically exact support recovery in the sense of \eqref{eq:support-recovery-success}.\\

{\rm (ii)} Conversely, if $\overline{r} < {{g}}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, we have $\P[\widehat{S}_p=S_p]\to0$.
Therefore, in view of Lemma \ref{lemma:risk-exact-recovery-probability}, exact support recovery asymptotically fails for all thresholding procedures in the sense of \eqref{eq:support-recovery-failure}.
\end{theorem}

@@

\begin{theorem} \label{thm:chi-squared-exact-approx-boundary}
In the context of Theorem \ref{thm:chi-squared-exact-boundary}, 
the function 
\begin{equation} \label{eq:exact-approx-boundary-chisquared}
    \widetilde{g}(\beta) = 1
\end{equation}
characterizes the phase transition of exact-approximate support recovery problem.
 Namely, the following two results hold.\\

{\rm (i)} If $\underline{r} > \widetilde{g}(\beta)$, then the procedures listed in Theorem \ref{thm:chi-squared-exact-boundary} with slowly 
vanishing nominal FWER levels achieve asymptotically exact-approximate support recovery in the sense of \eqref{eq:support-recovery-success}. \\

{\rm (ii)} Conversely, if $\overline{r} < \widetilde{g}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, the exact-approximate support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
\end{theorem}

@@

\begin{theorem} \label{thm:chi-squared-approx-boundary}
Consider the high-dimensional chi-squared model \eqref{eq:model-chisq-Chapter6} with signal sparsity and size as described in \eqref{eq:signal-sparsity} and \eqref{eq:signal-size}.
The function 
\begin{equation} \label{eq:approx-boundary-chisquared}
    h(\beta) = \beta
\end{equation}
characterizes the phase transition of approximate support recovery problem. Specifically the following two results hold.\\

{\rm (i)} If $\underline{r} > {h}(\beta)$, then the \ac{BH} procedure $\widehat{S}_p$ (defined in Section \ref{sec:statistical-procedures}) with slowly vanishing (see Definition \ref{def:slowly-vanishing}) nominal FDR levels achieves asymptotically approximate support recovery in the sense of \eqref{eq:support-recovery-success}. \\

{\rm (ii)} Conversely, if $\overline{r} < {h}(\beta)$, then approximate support recovery asymptotically fails in the sense of \eqref{eq:support-recovery-failure} for all thresholding procedures.
\end{theorem}

@@

\begin{theorem} \label{thm:chi-squared-approx-exact-boundary}
In the context of Theorem \ref{thm:chi-squared-approx-boundary}, the function 
\begin{equation} \label{eq:approx-exact-boundary-chisquared}
    \widetilde{h}(\beta) = \left(\sqrt{\beta} + \sqrt{1-\beta}\right)^2
\end{equation}
characterizes the phase transition of approximate-exact support recovery problem. Namely, 
the following two results hold.\\

{\rm (i)} If $\underline{r} > \widetilde{h}(\beta)$, then the Benjamini-Hochberg procedure with slowly vanishing nominal FDR levels achieves asymptotically approximate-exact support recovery in the sense of \eqref{eq:support-recovery-success}. \\

{\rm (ii)} Conversely, if $\overline{r} < \widetilde{h}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, the approximate-exact support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
\end{theorem}

>>>>

\begin{theorem} \label{thm:chi-squared-exact-boundary}
Consider the high-dimensional chi-squared model \eqref{eq:model-chisq-Chapter6} with signal sparsity and size as described in \eqref{eq:signal-sparsity} and \eqref{eq:signal-size}.
The function 
\begin{equation} \label{eq:exact-boundary-chisquared}
    f_{\mathrm{E}}(\beta) = \left(1 + \sqrt{1-\beta}\right)^2
\end{equation}
characterizes the phase transition of exact support recovery problem.
Namely, the following two results hold.\\

{\rm (i)} If $\underline{r} > f_{\mathrm{E}}(\beta)$, then Bonferroni's, Sid\'ak's, Holm's, and Hochberg's procedures with slowly vanishing (see Definition \ref{def:slowly-vanishing}) nominal FWER levels all achieve asymptotically exact support recovery in the sense of \eqref{eq:support-recovery-success}.\\

{\rm (ii)} Conversely, if $\overline{r} < f_{\mathrm{E}}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, we have $\P[\widehat{S}_p=S_p]\to0$.
Therefore, in view of Lemma \ref{lemma:risk-exact-recovery-probability}, exact support recovery asymptotically fails for all thresholding procedures in the sense of \eqref{eq:support-recovery-failure}.
\end{theorem}

@@

\begin{theorem} \label{thm:chi-squared-exact-approx-boundary}
In the context of Theorem \ref{thm:chi-squared-exact-boundary}, 
the function 
\begin{equation} \label{eq:exact-approx-boundary-chisquared}
    f_{\mathrm{EA}}(\beta) = 1
\end{equation}
characterizes the phase transition of exact-approximate support recovery problem.
 Namely, the following two results hold.\\

{\rm (i)} If $\underline{r} > f_{\mathrm{EA}}(\beta)$, then the procedures listed in Theorem \ref{thm:chi-squared-exact-boundary} with slowly 
vanishing nominal FWER levels achieve asymptotically exact-approximate support recovery in the sense of \eqref{eq:support-recovery-success}. \\

{\rm (ii)} Conversely, if $\overline{r} < f_{\mathrm{EA}}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, the exact-approximate support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
\end{theorem}

@@

\begin{theorem} \label{thm:chi-squared-approx-boundary}
Consider the high-dimensional chi-squared model \eqref{eq:model-chisq-Chapter6} with signal sparsity and size as described in \eqref{eq:signal-sparsity} and \eqref{eq:signal-size}.
The function 
\begin{equation} \label{eq:approx-boundary-chisquared}
    f_{\mathrm{A}}(\beta) = \beta
\end{equation}
characterizes the phase transition of approximate support recovery problem. Specifically the following two results hold.\\

{\rm (i)} If $\underline{r} > f_{\mathrm{A}}(\beta)$, then the \ac{BH} procedure $\widehat{S}_p$ (defined in Section \ref{sec:statistical-procedures}) with slowly vanishing (see Definition \ref{def:slowly-vanishing}) nominal FDR levels achieves asymptotically approximate support recovery in the sense of \eqref{eq:support-recovery-success}. \\

{\rm (ii)} Conversely, if $\overline{r} < f_{\mathrm{A}}(\beta)$, then approximate support recovery asymptotically fails in the sense of \eqref{eq:support-recovery-failure} for all thresholding procedures.
\end{theorem}

@@

\begin{theorem} \label{thm:chi-squared-approx-exact-boundary}
In the context of Theorem \ref{thm:chi-squared-approx-boundary}, the function 
\begin{equation} \label{eq:approx-exact-boundary-chisquared}
    f_{\mathrm{AE}}(\beta) = \left(\sqrt{\beta} + \sqrt{1-\beta}\right)^2
\end{equation}
characterizes the phase transition of approximate-exact support recovery problem. Namely, 
the following two results hold.\\

{\rm (i)} If $\underline{r} > f_{\mathrm{AE}}(\beta)$, then the Benjamini-Hochberg procedure with slowly vanishing nominal FDR levels achieves asymptotically approximate-exact support recovery in the sense of \eqref{eq:support-recovery-success}. \\

{\rm (ii)} Conversely, if $\overline{r} < f_{\mathrm{AE}}(\beta)$, then for any thresholding procedure $\widehat{S}_p$, the approximate-exact support recovery fails in the sense of \eqref{eq:support-recovery-failure}.
\end{theorem}

### 2021-04-04 7.GWAS/7.numerical.tex
many changes... Chapter 4 intro WIP

We illustrate with simulations the phase transition phenomena in the chi-square model, and compare numerically the required signal sizes in support recovery problems between the two types of alternatives in the additive error model.  
\stilian{These results can provide further guidance to practitioners on when to expect genetic association discoveries.
They provide also an explanation of the empirically observed phenomenon known as steep part of the power curve
in statistical genetics \citep{bush2012genome}. }{\fbox{IS this the RIGHT reference?  I could not find the ``steep part of the power curve" anywhere.}}
% We also demonstrate the fundamental trade-off between odds ratios and relative frequencies in association studies, as outlined in Proposition \ref{prop:signal-size-odds-ratio} and Corollary \ref{cor:signal-size-odds-ratio-conditional-frequency}, using evidence from large-scale genetic studies.

>>>>

We illustrate with simulations the phase transition phenomena in the chi-square model, and compare numerically the required signal sizes in support recovery problems between the two types of alternatives in the additive error model.  
% These results can provide further guidance to practitioners on when to expect genetic association discoveries. 
% We also demonstrate the fundamental trade-off between odds ratios and relative frequencies in association studies, as outlined in Proposition \ref{prop:signal-size-odds-ratio} and Corollary \ref{cor:signal-size-odds-ratio-conditional-frequency}, using evidence from large-scale genetic studies.

### 2021-04-04 7.GWAS/7.odds-and-power.tex
many changes... Chapter 4 intro WIP

In order to do so, we must first connect the concept of ``statistical signal size'' $\lambda$ with some key quantities in association tests.
While ``signal size'' likely sounds foreign to most practitioners, it is intimately linked with the concept of ``effect sizes'' --- or odds ratios --- in association studies, which are frequently estimated and reported in GWAS catalogs.
We characterize the relationship between the two quantities in the special, but fairly common case of association tests on 2-by-2 contingency tables in Section \ref{sec:odds-and-power}.

@@

Consider a 2-by-2 multinomial distribution with marginal probabilities of phenotypes $(\phi_1, \phi_2)$ and genotypes $(\theta_1, \theta_2)$.
The \emph{probability} table (as opposed to the table of multinomial \emph{counts} in the introduction) is as follows.
\begin{center}
    \begin{tabular}{cccc}
    \hline
    & \multicolumn{2}{c}{Genotype} \\
    \cline{2-3}
    Probabilities & Variant 1 & Variant 2 & Total by phenotype \\
    \hline
    Cases & $\mu_{11}$ & $\mu_{12}$ & $\phi_1$ \\
    Controls & $\mu_{21}$ & $\mu_{22}$ & $\phi_2$ \\
    Total by genotype & $\theta_1$ & $\theta_2$ & 1 \\
    \hline
    \end{tabular}
\end{center}
The odds ratio (i.e., ``effect size'') is defined as the ratio of the phenotype frequencies between the two genotype variants,
\begin{equation} \label{eq:odds-ratio}
    \text{R} := \frac{\mu_{11}}{\mu_{21}}\Big/\frac{\mu_{12}}{\mu_{22}}
    = \frac{\mu_{11}\mu_{22}}{\mu_{12}\mu_{21}}.
\end{equation}
The multinomial distribution is fully parametrized by the trio $(\theta_1, \phi_1, R)$.
Odds ratios further away from 1 indicate greater contrasts between the probability of outcomes.
Independence between the genotypes and phenotypes would imply an odds ratio of one, and hence $\mu_{jk} = \phi_j\theta_k$, for all $j,k \in\{1,2\}$.

>>>>

In order to do so, we must first connect the concept of statistical signal size $\lambda$ with some key quantities in association tests.
While the term ``signal size'' likely sounds foreign to most practitioners, it is intimately linked with the concept of ``effect sizes'' --- or odds ratios --- in association studies, which are frequently estimated and reported in GWAS catalogs. 
Effect sizes, on the other hand, may be alien to some statisticians.  
In this section, we aim to bridge the two languages by characterizing the relationship between ``signal size'' and ``odds-ratio'' parameterizations in the special, but fairly common case of association tests on 2-by-2 contingency tables.

 %in Section \ref{sec:odds-and-power}.

@@

Recall the general setup of genetic association testing in Section \ref{sec:motivation-chisq}, where one wants to detect the association between genetic variations at a specific location and the occurrence of a disease. 
An individual randomly drawn from the target population will have two (random) characteristics: a phenotype indicating whether the individual has the condition or is healthy (i.e., belonging to the Case group or the Control group), and a genotype that encodes the genetic variation in question. 
Table \ref{tab:multinomial-counts} in the introduction summarizes the {\em counts} for all phenotype-genotype combinations for the individuals in a given study sampled from the population.
These counts may be assumed to follow a multinomial distribution, with probabilities given in Table \ref{tab:multinomial-probabilites} below. 
% Notice that there are fundamental study design questions here since the counts will depend on the way individuals are recruited in the study. 
% For example, ``controlling'' the number of Cases or Controls (as opposed to sampling at random from the population) will change the theoretical parameters (probabilities) of the multinomial model.
% These questions will be addressed in Section \ref{sec:optimal-design} below.

Consider a 2-by-2 multinomial distribution with marginal probabilities of phenotypes $(\phi_1, \phi_2)$ and genotypes $(\theta_1, \theta_2)$.
The \emph{probability} table (as opposed to the table of multinomial \emph{counts} in the introduction) is as follows.
\begin{table}[h]\label{tab:multinomial-probabilites}
\begin{center}
    \begin{tabular}{cccc}
    \hline
    & \multicolumn{2}{c}{Genotype} \\
    \cline{2-3}
    Probabilities & Variant 1 & Variant 2 & Total by phenotype \\
    \hline
    Cases & $\mu_{11}$ & $\mu_{12}$ & $\phi_1$ \\
    Controls & $\mu_{21}$ & $\mu_{22}$ & $\phi_2$ \\
    Total by genotype & $\theta_1$ & $\theta_2$ & 1 \\
    \hline
    \end{tabular}
    \caption{Probabilities of the multinomial distribution in a genetic association test. (Compare and contrast with 
    Table \ref{tab:multinomial-counts}. We have $\E[ O_{ij}] = n\mu_{ij},\ i,j=1,2$, where $n = \sum_{i,j} O_{ij}$.) }
\end{center}
\end{table}

The odds ratio (i.e., ``effect size'') is defined as the ratio of the phenotype frequencies between the two genotype variants,
\begin{equation} \label{eq:odds-ratio}
    \text{R} := \frac{\mu_{11}}{\mu_{21}}\Big/\frac{\mu_{12}}{\mu_{22}}
    = \frac{\mu_{11}\mu_{22}}{\mu_{12}\mu_{21}}.
\end{equation}
The multinomial distribution is fully parametrized by the trio $(\theta_1, \phi_1, R)$.
Odds ratios further away from 1 indicate greater contrasts between the probability of outcomes.
Independence between the genotypes and phenotypes would imply an odds ratio of one, and hence $\mu_{jk} = \phi_j\theta_k$, for all $j,k \in\{1,2\}$.

### 2021-04-04 7.GWAS/GWAS.tex
many changes... Chapter 4 intro WIP

The process of scientific discovery, as famously explained by Richard Feynman, usually starts with guesses in one form or another.
The consequences of such guesses are then computed, and compared with experimental results.
If the predictions disagree with the experiment, then our guesses are wrong. ``That is all there is to it''  \citep{feynman2017character}.

In the previous chapters, we delved deep into the theoretical underpinnings of the phase transition phenomena in high-dimensional multiple testing problems.
The results are interesting in their own right.
However, in the spirit of Feynman, we have not discovered any scientific law, but merely worked out mathematical consequences of our postulated models.
In this chapter, our goal is to relate these predictions to real experimental data from the field of genetics, where large-scale simultaneous hypotheses testing problems often arise.
From such comparisons, we will demonstrate that the phase transition laws are indeed accurate predictions of some curious phenomena in the real world.
The accuracy of our predictions will lend credibility to the application of these ``laws of large dimensions'' in actual statistical problems.

@@

We then translate the canonical signal size and sparsity parametrizations into the vernacular of statistical geneticists in Section \ref{sec:odds-and-power}.
% present empirical evidence for the phase transition in the exact-approximate problem using real data from large-scale association studies on breast cancer obtained from the NHGRI-EBI GWAS Catalog \citep{macarthur2016new}.
% demystify the notion of signal size $\lambda$ in this context.
% which is perhaps less transparent than in additive error models.
We do so by characterizing the relationship between the signal size $\lambda$ and the marginal frequencies, odds ratio, and sample sizes for association tests on 2-by-2 contingency tables. 
These parameters are more often estimated and reported in \ac{GWAS} than the elusive signal size parameter $\lambda$.
% Specifically, the amount of signal, when rare variants are present, is weaker compared to the signal when the marginal distributions are balanced.
% In other words, reliable detection of the effects by rare variants would require more samples compared to common variants, even at the same odds ratio.
% This result, establishing the relationship between sample sizes and signal sizes, is made precise in Section \ref{sec:odds-and-power}.
As a bonus, we point out the implications of this relationship on statistically optimal study designs for association studies in Section \ref{sec:optimal-design}.
Perhaps surprisingly, our analysis reveals that balanced designs with equal number of cases and controls are often statistically inefficient.
% Practical consequences of these results in power analysis will be illustrated with data examples in Section \ref{sec:phase-transitions-in-GWAS}.

Armed with the results on phase transitions in the chi-square model, and a translation from the language of high-dimenstional statistics to the {\em patois} of association screening studies, we finally present in Section \ref{sec:phase-transitions-in-GWAS} the consequences of the phase transitions in \ac{GWAS}, and compare against real experimental data to evaluate the success of our predictions.

The phase transitions in the chi-square models are demonstrated with numerical simulations in Section \ref{sec:numerical}.
The proofs, which are closely related to those of the results in Chapter \ref{chap:phase-transitions},
 are collected in Section \ref{sec:supplement:proofs}.
%in Section \ref{sec:proof-signal-size-odds-ratio}.

>>>>

The process of scientific discovery, as explained by Richard Feynman, usually starts with guesses.
The consequences of such guesses are then computed and compared with experimental results.
If the predictions disagree with the experiment then our guesses are wrong. ``That is all there is to it''  \citep{feynman2017character}.

In the previous chapters, we delved deep into the theoretical underpinnings of the phase transition phenomena in high-dimensional multiple testing problems.
The results are interesting in their own right.
However, in the spirit of Feynman, we have not discovered any scientific law, but merely worked out mathematical consequences of our postulated models.
In this chapter, our goal is to relate these predictions to real experimental data from the field of genetics, where large-scale simultaneous hypotheses testing problems often arise.
From such comparisons, we will demonstrate that the phase transition laws are indeed reasonable predictions of some curious phenomena in that field.
The accuracy of our predictions will lend credibility to the application of these ``laws of large dimensions'' in actual applications.

@@

In the second step, we translate the canonical signal size and sparsity parametrizations into the vernacular of statistical geneticists in Section \ref{sec:odds-and-power}.
% present empirical evidence for the phase transition in the exact-approximate problem using real data from large-scale association studies on breast cancer obtained from the NHGRI-EBI GWAS Catalog \citep{macarthur2016new}.
% demystify the notion of signal size $\lambda$ in this context.
% which is perhaps less transparent than in additive error models.
We do so by characterizing the relationship between the signal size $\lambda$ and the marginal frequencies, odds ratio, and sample sizes for association tests on 2-by-2 contingency tables. 
This is important because these parameters are often estimated and reported in \ac{GWAS}, while we have never seen the elusive signal size parameter $\lambda$ reported.
% Specifically, the amount of signal, when rare variants are present, is weaker compared to the signal when the marginal distributions are balanced.
% In other words, reliable detection of the effects by rare variants would require more samples compared to common variants, even at the same odds ratio.
% This result, establishing the relationship between sample sizes and signal sizes, is made precise in Section \ref{sec:odds-and-power}.
As a bonus, we point out the implications of this relationship on statistically optimal study designs for association studies in Section \ref{sec:optimal-design}:
perhaps surprisingly, balanced designs with equal number of cases and controls are often statistically inefficient.
% Practical consequences of these results in power analysis will be illustrated with data examples in Section \ref{sec:phase-transitions-in-GWAS}.

Armed with the results on phase transitions in the chi-square model, and a translation from the language of high-dimenstional statistics to the patois of association screening studies, we finally present in Section \ref{sec:phase-transitions-in-GWAS} the consequences of the phase transitions in \ac{GWAS}, and compare against real experimental data to evaluate the success of our predictions.

The phase transitions in the chi-square models are demonstrated with numerical simulations in Section \ref{sec:numerical}.
The proofs, which are closely resemble those of the results in Chapter \ref{chap:phase-transitions}, are collected in Section \ref{sec:supplement:proofs}.
%in Section \ref{sec:proof-signal-size-odds-ratio}.

### 2021-04-04 supplement/other-boundaries.tex
many changes... Chapter 4 intro WIP

We would like to point out that the sparsity and signal sizes can be re-parametrized for the boundaries to have different shapes.
For example in the case of Gaussian errors, if we re-parametrize sparsity $s$ with 
$\widetilde{\beta} = 2 - \left(1 + \sqrt{1-\beta}\right)^2$ where $\widetilde{\beta}\in(0,1)$, then the signal sparsity would have a slightly more complicated form:
$$
\left|S_p\right| = \left\lfloor p^{1-\beta} \right\rfloor = \left\lfloor p^{\left(\sqrt{2 - \widetilde{\beta}} - 1\right)^2}\right\rfloor,
$$
while the strong classification boundary would take on the simpler form:
\begin{equation}\label{eq:altenative-parametrization}
g(\beta) = \widetilde{g}(\widetilde{\beta}) = 2 - \widetilde{\beta}.
\end{equation}
In the next two classes of models we will adopt parametrizations such that the boundaries are of the form $\widetilde{g}$ in \eqref{eq:altenative-parametrization}.

@@

\begin{theorem} \label{thm:heavier-than-AGG}
Suppose the marginals $F$ follows \eqref{eq:heavier-than-AGG-boundary-1} and \eqref{eq:heavier-than-AGG-boundary-2}.
Let
$$
k(\beta) = \log{p} - \left((\log{p})^{1/\gamma} + \log{(1-\beta)}\right)^\gamma,
$$
and let the signal $\mu$ have 
$$|S_p| = \left\lfloor pe^{-k(\beta)} \right\rfloor$$
non-zero entries. Assume the magnitudes of non-zero signal entries are in the range between
$$\underline{\Delta} = \exp{\left\{(\log{p})^{1/\gamma}\right\}}\underline{r}
\quad\text{and}\quad
\overline{\Delta} = \exp{\left\{(\log{p})^{1/\gamma}\right\}}\overline{r}.$$
If $\underline{r} > \widetilde{g}(\beta) = 2 - \beta$, then Bonferroni's procedure $\widehat{S}_p$ (defined in \eqref{eq:Bonferroni-procedure}) with appropriately calibrated FWER $\alpha\to 0$ achieves asymptotic perfect support recovery, under arbitrary dependence of the errors.

On the other hand, when the errors are uniformly relatively stable, if $\overline{r} < \widetilde{g}(\beta) = 2 - \beta$, then no thresholding procedure can achieve asymptotic perfect support recovery with positive probability.
\end{theorem}

@@

\begin{theorem} \label{thm:lighter-than-AGG}
Suppose marginals $F$ follow \eqref{eq:lighter-than-AGG-boundary-1} and \eqref{eq:lighter-than-AGG-boundary-2}.
Let
$$
k(\beta) = \log{p} - \left(\log(p)\right)^{(1-\beta)^\nu},
$$
and let the signal $\mu$ have 
$$|S_p| = \left\lfloor pe^{-k(\beta)} \right\rfloor$$
non-zero entries. Assume the magnitudes of non-zero signal entries are in the range between
$$\underline{\Delta} = \log{\log{p}}^{1/\nu}\underline{r}
\quad\text{and}\quad
\overline{\Delta} = \log{\log{p}}^{1/\nu}\overline{r}.$$
If $\underline{r} > \widetilde{g}(\beta) = 2 - \beta$, then Bonferroni's procedure $\widehat{S}_p$ (defined in \eqref{eq:Bonferroni-procedure}) with appropriately calibrated FWER $\alpha\to 0$ achieves asymptotic perfect support recovery, under arbitrary dependence of the errors.

On the other hand, when the errors are uniformly relatively stable, if $\overline{r} < \widetilde{g}(\beta) = 2 - \beta$, then no thresholding procedure can achieve asymptotic perfect support recovery with positive probability.
\end{theorem}

>>>>

We would like to point out that the sparsity and signal sizes can be re-parametrized for the boundaries to have different shapes.
For example in the case of Gaussian errors, if we re-parametrize sparsity $s$ with 
$\widetilde{\beta} = 2 - \left(1 + \sqrt{1-\beta}\right)^2$ where $\widetilde{\beta}\in(0,1)$, then the signal sparsity would have a slightly more complicated form:
$$
\left|S_p\right| = \left\lfloor p^{1-\beta} \right\rfloor = \left\lfloor p^{\left(\sqrt{2 - \widetilde{\beta}} - 1\right)^2}\right\rfloor,
$$
while the strong classification boundary would take on the simpler form:
\begin{equation}\label{eq:altenative-parametrization}
f_{\mathrm{E}}(\beta) = \widetilde{f}_{\mathrm{E}}(\widetilde{\beta}) = 2 - \widetilde{\beta}.
\end{equation}
In the next two classes of models we will adopt parametrizations such that the boundaries are of the form $\widetilde{g}$ in \eqref{eq:altenative-parametrization}.

@@

\begin{theorem} \label{thm:heavier-than-AGG}
Suppose the marginals $F$ follows \eqref{eq:heavier-than-AGG-boundary-1} and \eqref{eq:heavier-than-AGG-boundary-2}.
Let
$$
k(\beta) = \log{p} - \left((\log{p})^{1/\gamma} + \log{(1-\beta)}\right)^\gamma,
$$
and let the signal $\mu$ have 
$$|S_p| = \left\lfloor pe^{-k(\beta)} \right\rfloor$$
non-zero entries. Assume the magnitudes of non-zero signal entries are in the range between
$$\underline{\Delta} = \exp{\left\{(\log{p})^{1/\gamma}\right\}}\underline{r}
\quad\text{and}\quad
\overline{\Delta} = \exp{\left\{(\log{p})^{1/\gamma}\right\}}\overline{r}.$$
If $\underline{r} > \widetilde{f}_{\mathrm{E}}(\beta) = 2 - \beta$, then Bonferroni's procedure $\widehat{S}_p$ (defined in \eqref{eq:Bonferroni-procedure}) with appropriately calibrated FWER $\alpha\to 0$ achieves asymptotic perfect support recovery, under arbitrary dependence of the errors.

On the other hand, when the errors are uniformly relatively stable, if $\overline{r} < \widetilde{f}_{\mathrm{E}}(\beta) = 2 - \beta$, then no thresholding procedure can achieve asymptotic perfect support recovery with positive probability.
\end{theorem}

@@

\begin{theorem} \label{thm:lighter-than-AGG}
Suppose marginals $F$ follow \eqref{eq:lighter-than-AGG-boundary-1} and \eqref{eq:lighter-than-AGG-boundary-2}.
Let
$$
k(\beta) = \log{p} - \left(\log(p)\right)^{(1-\beta)^\nu},
$$
and let the signal $\mu$ have 
$$|S_p| = \left\lfloor pe^{-k(\beta)} \right\rfloor$$
non-zero entries. Assume the magnitudes of non-zero signal entries are in the range between
$$\underline{\Delta} = \log{\log{p}}^{1/\nu}\underline{r}
\quad\text{and}\quad
\overline{\Delta} = \log{\log{p}}^{1/\nu}\overline{r}.$$
If $\underline{r} > \widetilde{f}_{\mathrm{E}}(\beta) = 2 - \beta$, then Bonferroni's procedure $\widehat{S}_p$ (defined in \eqref{eq:Bonferroni-procedure}) with appropriately calibrated FWER $\alpha\to 0$ achieves asymptotic perfect support recovery, under arbitrary dependence of the errors.

On the other hand, when the errors are uniformly relatively stable, if $\overline{r} < \widetilde{f}_{\mathrm{E}}(\beta) = 2 - \beta$, then no thresholding procedure can achieve asymptotic perfect support recovery with positive probability.
\end{theorem}
